Species sympatry shapes brain size evolution in Primates

### 2022-01-28 Article/Article_forsubmission_wordworking.Rmd
Update for submission - Separation Sup mat and Main text - Add Rmd word compilation

output: 
 #      - '--lua-filter=scholarly-metadata.lua'
 #      - '--lua-filter=author-info-blocks.lua'
 bookdown::pdf_book:
 #bookdown::word_document2:
   number_sections: false
   toc: false
   citation_package: biblatex
   latex_engine: pdflatex
   fig_caption: true
   #pandoc_args:
     #- '--lua-filter=scholarly-metadata.lua'
     #- '--lua-filter=author-info-blocks.lua'
 keep_tex: true
always_allow_html: true

@@

#Plot
library(RColorBrewer)
library(tidyr)
library(stringr)
library(svMisc)
library(plotrix)
library(circlize)

@@

<!-- Reviewer possibles: Decasien, Powell, Barton, Kamilar, Harmon, Drury -->
**Running title:** Species sympatry shapes primates' brain size  
\faTags \hspace{0.01in} **Keywords:** Brain size - Cognition - Competition - Co-occurrence - Diversification - Frugivory - Primates - Sympatry
<!-- \faInfoCircle  \hspace{0.01in} **Word Count:** `r words$num_words` \newline -->
<!-- Character Count: `r words$num_char` -->

@@

<!-- On the road to brain size evolution, generally considered as an equivalent of cognition evolution, mysteries are plenty [@van2006some; @dunbar2017there]. Overall, the evolution of the brain is the consequence of constraints (e.g. energetic limitations, @navarrete2011energetics), but also of socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference].  -->
<!-- Primates are pivotal species to study the evolution of cognition given the complexity of their socio-ecological environment and the inevitable implication for retracing human evolutionary history [@byrne2000evolution].  -->

<!-- \initial{\textcolor{black}{C}}ognition evolution results from the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints [@navarrete2011energetics]. Primates are pivotal species for cognitive studies [@byrne2000evolution] because their cognition is thought to be promoted by interactions of individuals with conspecifics within the social unit [@byrne1994machiavellian; @dunbar2017there], among generations [@wilson1991molecular; @whiten2007evolution; @reader2002social; @herrmann2007humans; @tomasello2009cultural; @van2011social], between social units [@ashton2020interactions], or with the rest of their environment [@clutton1980primates; @milton1981distribution; @rosati2017foraging]. However, space is a place often occupied by many species belonging to the same ecological guild and we can predict that such interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition. -->

<!-- |   Retracing the evolutionary history of cognitive abilities proves to be challenging because there is still no consensual measurement applicable across all species. Up to now, a raw approximation consists in considering brain size as a proxy for cognitive abilities (but see discussion in @logan2018beyond). Yet, the brain is a mosaic of areas cognitively specialized [@barton2000mosaic] and these areas are likely to be differently affected by species sympatry. For instance, the Main Olfactory Bulb (MOB) or the Hippocampus , home of a spatio-temporal memory [@burgess2002human], are largely involved in efficient foraging, especially for frugivorous primates, as fruits are the archetype of a hard-to-find resource yet predictable [@janmaat2016spatio; @robirabotany]: we therefore expect that primate species with larger MOB or Hippocampus areas, taken as equivalent to more advanced perceptive and cognitive abilities for efficient foraging, might be more fit than their sympatric species with smaller areas. Similarly, the Striatum underpins reward expectation and action, goal-directed behaviour and planning abilities [@johnson2007integrating] which is key when foraging. -->
<!-- are expected to be influenced by the ecological environment. The Striatum is also stimulated during social interactions [@baez2013role]: its size is thus expected to be positively influenced when contacts with other species increase, as in species performing mixed-species groups, which is nonetheless rather infrequent in primates (but see callitrichine primates in particular, @heymann2015unlike). Finally, besides foraging-related areas (Striatum, MOB or Hippocampus), more generally-used areas, such as the Cerebellum [@koziol2014consensus; @sokolov2017cerebellum] and the Neocortex [@wiltgen2004new] underlying movement and/or general information processing and retention, could also be stimulated by the presence of other species movement traces, noises or odors to decode. To sum up, a first possibility is that sympatric heterospecifics could altogether stimulate cognition and promote larger sizes of the brain areas related to interacting with the social or ecological environment.  -->

<!-- |   However, if the changes induced by sympatric species increases the environmental unpredictability too much, sympatry could on the contrary change the selective pressure applying to cognitive abilities [@grove2013evolution: @robirainreview]. Indeed, due to the cost of maintaining the brain functional [@raichle2006brain], it is expected that the increase in environmental unpredictability only stimulates cognition up to a certain threshold (i.e. positive selection for bigger brain), before smaller brain sizes of foraging-related areas become more adaptive (because costs are no longer compensated by the benefit of memory). Similarly, it is possible that processing heterospecifics cues, and other environmental cues (e.g. phenology cues) might not necessitate the same cognition level, with the former being potentially simpler to process (since relying on easily accessible social cues) than the latter (relying on trial-and-error processes and personal experience of potentially elusive environmental cues) [@laland2004social]. In this case, the size of brain areas involved in immediate information processing should be less large in sympatric than in non-sympatric conditions. To sum up, a second possibility is that sympatric heterospecifics could hamper the benefits of cognition on foraging, and thus slowdown brain size increase. In an extreme case, it could even induce positive selection for smaller brain size. -->

<!-- |    Here, we investigated the intertwine between species sympatry and cognition using frugivorous primates as study example. To infer the effect of species interactions on brain size evolution within frugivorous primates, we evaluated support for competitive or non-competitive evolutionary scenarios, accounting or not for sympatry, and investigated the directionality of the selection induced by sympatry history upon brain size evolution. Finally, we tested for correlative patterns between brain size or current sympatry with the evolutionary success (species diversification) in primates. -->

\initial{\textcolor{black}{C}}ognition evolution is shaped by the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints limiting them [@navarrete2011energetics]. Primates are pivotal species for cognitive studies [@byrne2000evolution] because their cognition is thought to be promoted by interactions of individuals with conspecifics within the social unit [@byrne1994machiavellian; @dunbar2017there], among generations [@wilson1991molecular; @whiten2007evolution; @reader2002social; @herrmann2007humans; @tomasello2009cultural; @van2011social], between social units [@ashton2020interactions], or with the rest of their environment [@clutton1980primates; @milton1981distribution; @rosati2017foraging]. However, space is often occupied by many species belonging to the same ecological guild. Because of competition for food, we can predict that indirect interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition, because they either affect the resource landscape by depleting it (Hypothesis 1), or the landscape of usable “social” cues to locate available food [@Avargues-Weber2013, Hypothesis 2]. In addition, direct interactions with heterospecifics, as much as with conspecifics [@dunbar2017there], might also affect cognition (Hypothesis 3).

@@

@@

Data were pooled from previous literature surveys (see Appendix [Data availability]). Brain data were obtained from @decasien2019primate for the  whole brain and all mentioned other regions (Cerebellum, Hippocampus, Main Olfactory Bulb (MOB), Neocortex, Striatum), @powell2017re and @powell2019maternal for the whole brain, Cerebellum and Neocortex size, @todorov2019primate for Hippocampus and Neocortex size, @grueter2015home for the whole brain size and @navarrete2018primate for the whole brain, Cerebellum, Hippocampus and Striatum size. They were freely available in the main manuscript or supplementary materials. Percentage of frugivory and/or folivory was obtained based on a freely available dataset from @decasien2017primate, @powell2017re, and @willems2013collective. Availability of trait and distribution range for the `r length(phylo_init$tip.label)` primate species represented in the primate phylogeny of the 10kTrees project is depicted in Appendix Fig. S3. From the global endocranial brain volume, we obtained the Encephalization Quotient (EQ, N$_{EQ,max}$ = `r maxEQ`) as follows [@decasien2017primate]

@@

\begin{center}

@@

\end{center}

@@

We focused only on frugivorous primates and fitted phylogenetic models of the evolution of the size of the different brain areas. The models were based on different sample sizes depending on the brain areas and the frugivory thresholds considered: EQ: `r minEQ` to `r maxEQ`, Striatum: `r minStriatum` to `r maxStriatum`, MOB: `r minMOB` to `r maxMOB`, Neocortex: `r minNeocortex` to `r maxNeocortex`, Hippocampus: `r minHippocampus` to `r maxHippocampus`, Cerebellum: `r minCerebellum` to `r maxCerebellum` frugivorous species. For each set of models in a given brain area, the sample was strictly identical, allowing within-set comparisons. Prior to fitting, trait parameters were log-transformed to reach more symmetrical distributions. We calculated the likelihoods of models considering the role of species sympatry in the evolution of either the whole brain (using the encephalic quotient, EQ), or the size of the aforementioned specific brain areas relative to the whole-body mass (Figure \@ref(fig:figbrain)). We specifically considered three different models considering species sympatry: the matching competition (MC) model [@nuismer2015predicting] and density-dependent models [DD$_{lin}$ and DD$_{exp}$, @drury2016estimating]. These models notably account for interspecific interaction matrices that are built on the evolutionary history of species sympatry and diet. These interaction matrices retrace, along the phylogenetic tree, which frugivorous lineages were present within the same geographic areas [see @drury2016estimating]. The matching competition model (MC) considers the repulsion of traits of sympatric lineages from the same dietary guild due to competition (character displacement) [@drury2016estimating]. Here, that would mean that sympatric species would tend to divergently evolve either lower, or higher, EQ or relative brain size. Otherwise, we modelled trait evolution accounting for linear (DD$_{lin}$) or exponential (DD$_{exp}$) density-dependence [@drury2016estimating; @weir2013diversity]. Density-dependence means that the evolutionary rate, $\lambda$, of trait change, varies either positively or negatively as a function $f$ of the number of frugivorous sympatric lineages, such as

\begin{center}

@@

rownames(results.df_gradient) <- NULL
knitr::kable(results.df_gradient, escape=TRUE, booktabs = TRUE, caption = "Species sympatry correlates negatively with the sizes of some brain areas : Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value. The brain areas (as well as the associated sample size) are indicated prior to each list of estimates. The transformation applied to variables are indicated between brackets (logarithm, log, or square-root, sqrt), as well as the ponderation by bodymass (/bodymass).") %>%
  kableExtra::column_spec(2:ncol(results.df_gradient), bold = toPlotBold[-(6:10)]) %>% #Remove brain raw
  kableExtra::kable_styling(latex_options = "striped") %>%
  kableExtra::kable_styling(latex_options="scale_down") #%>%
  #kableExtra::kable_styling(latex_options = "HOLD_position")

# as_huxtable(results.df_gradient) %>%
#   set_caption("Species sympatry correlates negatively with the sizes of some brain areas : Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value. The brain areas (as well as the associated sample size) are indicated prior to each list of estimates. The transformation applied to variables are indicated between brackets (logarithm, log, or square-root, sqrt), as well as the ponderation by bodymass (/bodymass).") %>%
# 
#   
# #Bold row with p-value < 0.05
# set_bold(row = which(toPlotBold[-(6:10)]), col = 2:ncol(results.df_gradient)) %>%
# 
# #Main layout
# set_bottom_border(row = 1, col = everywhere) %>% 
# set_bold(row = 1, col = everywhere) %>% 
# set_background_color(evens, everywhere, "grey95") %>%
# as_flextable() %>%

@@

```{r tableRegDiversification, include=TRUE}
results.df_diversification <- results.df_diversification[-(5:8),]
rownames(results.df_diversification) <- NULL
knitr::kable(results.df_diversification, escape=TRUE, booktabs = TRUE, caption = "The relative brain sizes  did not impact primate species diversification: Model estimates and significance of Bayesian phylogenetic regressions to assess the correlation between the net diversification rates and the relative brain sizes | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff. samp.=Effective sample (adjusted for autocorrelation). The brain areas (as well as the associated sample size) are indicated prior to each list of estimates. The logarithm transformation was applied to variable and is indicated between brackets (log), as well as the ponderation by bodymass (/bodymass).") %>%
  kableExtra::column_spec(2:ncol(results.df_diversification), bold = toPlotBoldDiversification[-(5:8)]) %>% #Remove brain raw
  kableExtra::kable_styling(latex_options = "striped") %>%
  kableExtra::kable_styling(latex_options="scale_down") #%>%
  #kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

knitr::kable(results.df_diversificationAndSympatry, escape=TRUE, booktabs = TRUE,  caption = "Species sympatry slowdowns primate diversification: Model estimates and significance of phylogenetic regressions to assess the correlation between diversification rate and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd= Standard deviation, t= Statistics t-value. The brain areas (as well as the associated sample size) are indicated prior to each list of estimates. The transformation (logarithm or square-root) is indicated in parentheses by the abbreviation (log or sqrt).") %>%
  kableExtra::column_spec(2:ncol(results.df_diversificationAndSympatry), bold = toPlotBoldSympatry) %>%
  kableExtra::kable_styling(latex_options = "striped") %>%
  kableExtra::kable_styling(latex_options="scale_down")

@@

par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
emptyPlot()
legend(x=0.15, y=1, yjust=1, horiz=TRUE, fill=c(adjustcolor("royalblue", alpha.f=0.2), adjustcolor("blue", alpha.f=0.2)), legend=c("Not considering species sympatry", "Considering species sympatry"), bty="n", cex=1.35)

save.image("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/RDataforAppendix.RData")
```

>>>>

output: 
 #      - '--lua-filter=scholarly-metadata.lua'
 #      - '--lua-filter=author-info-blocks.lua'
 #bookdown::pdf_book:
 bookdown::word_document2:
   number_sections: false
   toc: false
   citation_package: biblatex
   latex_engine: pdflatex
   fig_caption: true
   #pandoc_args:
     #- '--lua-filter=scholarly-metadata.lua'
     #- '--lua-filter=author-info-blocks.lua'
always_allow_html: true

@@

#Tables
library(huxtable)

#Plot
library(RColorBrewer)
library(tidyr)
library(stringr)
library(svMisc)
library(plotrix)
library(circlize)
library(magick)
library(knitr)
library(png)

@@

<!-- Reviewer possibles: Decasien, Powell, Barton, Kamilar, Harmon, Drury -->
**Running title:** Species sympatry shapes primates' brain size  
**Keywords:** Brain size - Cognition - Competition - Co-occurrence - Diversification - Frugivory - Primates - Sympatry
<!-- \faInfoCircle  \hspace{0.01in} **Word Count:** `r words$num_words` \newline -->
<!-- Character Count: `r words$num_char` -->

@@

  Cognition evolution is shaped by the balance between socio-ecological drivers promoting cognitive abilities [@gonzalez2018inference] and physiological and energetic constraints limiting them [@navarrete2011energetics]. Primates are pivotal species for cognitive studies [@byrne2000evolution] because their cognition is thought to be promoted by interactions of individuals with conspecifics within the social unit [@byrne1994machiavellian; @dunbar2017there], among generations [@wilson1991molecular; @whiten2007evolution; @reader2002social; @herrmann2007humans; @tomasello2009cultural; @van2011social], between social units [@ashton2020interactions], or with the rest of their environment [@clutton1980primates; @milton1981distribution; @rosati2017foraging]. However, space is often occupied by many species belonging to the same ecological guild. Because of competition for food, we can predict that indirect interactions with sympatric heterospecifics are also likely to strongly shape the evolution of cognition, because they either affect the resource landscape by depleting it (Hypothesis 1), or the landscape of usable “social” cues to locate available food [@Avargues-Weber2013, Hypothesis 2]. In addition, direct interactions with heterospecifics, as much as with conspecifics [@dunbar2017there], might also affect cognition (Hypothesis 3).

@@

## Data Collection

@@

Data were pooled from previous literature surveys (see Appendix [Data availability]). Data were pooled from previous literature surveys (see Appendix [Data availability]). Brain data were obtained from @decasien2019primate for the  whole brain and all mentioned other regions (Cerebellum, Hippocampus, Main Olfactory Bulb (MOB), Neocortex, Striatum), @powell2017re and @powell2019maternal for the whole brain, Cerebellum and Neocortex size, @todorov2019primate for Hippocampus and Neocortex size, @grueter2015home for the whole brain size and @navarrete2018primate for the whole brain, Cerebellum, Hippocampus and Striatum size. They were freely available in the main manuscript or supplementary materials. Percentage of frugivory and/or folivory was obtained based on a freely available dataset from @decasien2017primate, @powell2017re, and @willems2013collective. Availability of trait and distribution range for the `r length(phylo_init$tip.label)` primate species represented in the primate phylogeny of the 10kTrees project is depicted in Appendix Fig. S3. From the global endocranial brain volume, we obtained the Encephalization Quotient (EQ, N$_{EQ,max}$ = `r maxEQ`) as follows [@decasien2017primate]

@@

<!-- \begin{center} -->

@@

  <!-- \end{center} -->

@@

We focused only on frugivorous primates and fitted phylogenetic models of the evolution of the size of the different brain areas. The models were based on different sample sizes depending on the brain areas and the frugivory thresholds considered: EQ: `r minEQ` to `r maxEQ`, Striatum: `r minStriatum` to `r maxStriatum`, MOB: `r minMOB` to `r maxMOB`, Neocortex: `r minNeocortex` to `r maxNeocortex`, Hippocampus: `r minHippocampus` to `r maxHippocampus`, Cerebellum: `r minCerebellum` to `r maxCerebellum` frugivorous species. For a given set of models (i.e. within brain area), the sample was strictly identical, allowing within-set comparisons. Prior to fitting, trait parameters were log-transformed to reach more symmetrical distributions. We calculated the likelihoods of models considering the role of species sympatry in the evolution of either the whole brain (using the encephalic quotient, EQ), or the size of the aforementioned specific brain areas relative to the whole-body mass (Fig. \@ref(fig:figbrain)). We specifically considered three different models considering species sympatry: the matching competition (MC) model [@nuismer2015predicting] and density-dependent models [DD$_{lin}$ and DD$_{exp}$, @drury2016estimating]. These models notably account for interspecific interaction matrices that are built on the evolutionary history of species sympatry and diet. These interaction matrices retrace, along the phylogenetic tree, which frugivorous lineages were present within the same geographic areas [see @drury2016estimating]. The matching competition model (MC) considers the repulsion of traits of sympatric lineages from the same dietary guild due to competition (character displacement) [@drury2016estimating]. Here, that would mean that sympatric species would tend to divergently evolve either lower, or higher, EQ or relative brain size. Otherwise, we modelled trait evolution accounting for linear (DD$_{lin}$) or exponential (DD$_{exp}$) density-dependence [@drury2016estimating; @weir2013diversity]. Density-dependence means that the evolutionary rate, $\lambda$, of trait change, varies either positively or negatively as a function $f$ of the number of frugivorous sympatric lineages, such as

<!-- \begin{center} -->

@@

rownames(results.df_gradient) <- NULL
# knitr::kable(results.df_gradient, escape=TRUE, booktabs = TRUE, caption = "Species sympatry correlates negatively with the sizes of some brain areas : Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value. The brain areas (as well as the associated sample size) are indicated prior to each list of estimates. The transformation applied to variables are indicated between brackets (logarithm, log, or square-root, sqrt), as well as the ponderation by bodymass (/bodymass).") %>%
#   kableExtra::column_spec(2:ncol(results.df_gradient), bold = toPlotBold[-(6:10)]) %>% #Remove brain raw
#   kableExtra::kable_styling(latex_options = "striped") %>%
#   kableExtra::kable_styling(latex_options="scale_down") #%>%
#   #kableExtra::kable_styling(latex_options = "HOLD_position")

as_huxtable(results.df_gradient) %>%
  set_caption("Species sympatry correlates negatively with the sizes of some brain areas : Model estimates and significance of phylogenetic regressions to assess the relationship between relative brain sizes and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd=Standard deviation, t=Statistics t-value. The brain areas (as well as the associated sample size) are indicated prior to each list of estimates. The transformation applied to variables are indicated between brackets (logarithm, log, or square-root, sqrt), as well as the ponderation by bodymass (/bodymass).") %>%

#Bold row with p-value < 0.05
set_bold(row = which(toPlotBold[-(6:10)])+1, col = 2:ncol(results.df_gradient)) %>%

#Main layout
set_bottom_border(row = 1, col = everywhere) %>%
set_bold(row = 1, col = everywhere) %>%
set_background_color(evens, everywhere, "grey95") %>%
as_flextable()

@@

```{r tableRegDiversification, include=TRUE}
results.df_diversification <- results.df_diversification[-(5:8),]
rownames(results.df_diversification) <- NULL
# knitr::kable(results.df_diversification, escape=TRUE, booktabs = TRUE, caption = "The relative brain sizes  did not impact primate species diversification: Model estimates and significance of Bayesian phylogenetic regressions to assess the correlation between the net diversification rates and the relative brain sizes | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff. samp.=Effective sample (adjusted for autocorrelation). The brain areas (as well as the associated sample size) are indicated prior to each list of estimates. The logarithm transformation was applied to variable and is indicated between brackets (log), as well as the ponderation by bodymass (/bodymass).") %>%
#   kableExtra::column_spec(2:ncol(results.df_diversification), bold = toPlotBoldDiversification[-(5:8)]) %>% #Remove brain raw
#   kableExtra::kable_styling(latex_options = "striped") %>%
#   kableExtra::kable_styling(latex_options="scale_down") #%>%
#   #kableExtra::kable_styling(latex_options = "HOLD_position")
#

as_huxtable(results.df_diversification) %>%
  set_caption("The relative brain sizes  did not impact primate species diversification: Model estimates and significance of Bayesian phylogenetic regressions to assess the correlation between the net diversification rates and the relative brain sizes | Est.=Estimate, HDP2.5\\%=Lower border of the 95\\% Highest Posterior Density, HDP97.5\\%=Upper border of the 95\\% Highest Posterior Density, Eff. samp.=Effective sample (adjusted for autocorrelation). The brain areas (as well as the associated sample size) are indicated prior to each list of estimates. The logarithm transformation was applied to variable and is indicated between brackets (log), as well as the ponderation by bodymass (/bodymass).") %>%

#Bold row with p-value < 0.05
set_bold(row = which(toPlotBoldDiversification[-(5:8)])+1, col = 2:ncol(results.df_diversification)) %>%

#Main layout
set_bottom_border(row = 1, col = everywhere) %>%
set_bold(row = 1, col = everywhere) %>%
set_background_color(evens, everywhere, "grey95") %>%
as_flextable()
```

@@

# knitr::kable(results.df_diversificationAndSympatry, escape=TRUE, booktabs = TRUE,  caption = "Species sympatry slowdowns primate diversification: Model estimates and significance of phylogenetic regressions to assess the correlation between diversification rate and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd= Standard deviation, t= Statistics t-value. The brain areas (as well as the associated sample size) are indicated prior to each list of estimates. The transformation (logarithm or square-root) is indicated in parentheses by the abbreviation (log or sqrt).") %>%
#   kableExtra::column_spec(2:ncol(results.df_diversificationAndSympatry), bold = toPlotBoldSympatry) %>%
#   kableExtra::kable_styling(latex_options = "striped") %>%
#   kableExtra::kable_styling(latex_options="scale_down")

as_huxtable(results.df_diversificationAndSympatry) %>%
  set_caption("Species sympatry slowdowns primate diversification: Model estimates and significance of phylogenetic regressions to assess the correlation between diversification rate and species sympatry | Est.=Estimate, CI2.5\\%=Lower border of the CI95\\%, CI97.5\\%=Upper border of the CI95\\%, Sd= Standard deviation, t= Statistics t-value. The brain areas (as well as the associated sample size) are indicated prior to each list of estimates. The transformation (logarithm or square-root) is indicated in parentheses by the abbreviation (log or sqrt).") %>%

#Bold row with p-value < 0.05
set_bold(row = which(toPlotBoldSympatry)+1, col = 2:ncol(results.df_diversificationAndSympatry)) %>%

#Main layout
set_bottom_border(row = 1, col = everywhere) %>%
set_bold(row = 1, col = everywhere) %>%
set_background_color(evens, everywhere, "grey95") %>%
as_flextable()

@@

par(mar=c(0, 0, 0, 0), mgp=c(2, 0.5, 0), xpd=TRUE)
emptyPlot()
legend(x=0.15, y=1, yjust=1, horiz=TRUE, fill=c(adjustcolor("royalblue", alpha.f=0.2), adjustcolor("blue", alpha.f=0.2)), legend=c("Not considering species sympatry", "Considering species sympatry"), bty="n", cex=1.35)
```
